Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-18 journal/article.tex
Large scale

@@

A key question in this study was the definition of \emph{large scale}. Our goal
was to identify phenomena that appear particularly in large-scale
transformations, and which may not be present in small organizations. Large
scale requires additional coordination and makes communication difficult
compared to software development in small teams.

In this section we first present the definition of large scale.

--> Needs to have complexity in software design?? --> What is complexity in software?
    Is ``complexity'' an issue in agile?
    What will bring complexity into software? Not costs or the length of the
    schedule. --> Having many people will bring the complexity in terms of the
    SDM to use.
--> Some people see cost as a definition for large scale, some see code base
    size [Petersen], some see project duration [Bjarnson?]. These are all
    related, but do not relate to any specific problem. You can spend X amount
    of money, but it does not in itself make any difference if the money is
    spent in an agile way.
--> Formal definitions (EU, etc.) look at project costs or company turnover.
    These definitions do not take a standpoint on complexity of the product, so
    they do not matter in the context of SDMs.

--> Ref: the XP conference
--> [Cockburn 2003] Agile is best suitable for teams around 50 people or fewer.
--> Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
    Perplexed: Addison-Wesley, 2003. --> There might be a 50 person boundary?
    --> See Boehm also for list of

@@

Transformation and ``scaling up'' are very closely related and in some cases
they are one and the same. For instance, if transformation begins with a pilot
and spreads gradually through the organization, the process can very well be
seen as a ``scaling up'' journey. However, we excluded cases where a initially
small organization was scaled up \cite{Maranzato2012}, and discussions focusing
on processes or tools without describing organizational change \cite{Lyon2008}.
% Also [Greening 2010] on process centered viewpoint without transformation

@@

A further example on exclusion by the \emph{large scale} facet were cases with
large organizations but only a single team adopting agile \cite{Fulgham2011}.
We considered cases of single teams (although in large organizations) unrelated
to this research as our focus is on transformation of the entire organization.
Also piloting cases that resulted only in single teams using agile were excluded
\cite{Scott2008}.

@@

In addition to inter-team coordination there were also other challenges that
should only emerge in a sizable organization.
Most importantly, additional layers of management are usually necessary to steer
large groups of people. The problem is that agile methods provide little
guidance on how to organize management.
Problems may also arise in a large environment if the schedule of agile adoption
varies from team to team. Internal fragmentation is a further problem that may
be encountered in large organizations.
Table \label{table:challenges_largescale} summarizes these challenges.

>>>>

Dingsoyr:
The nature of software development, being innovative work that is only partially
compatible with programmed coordination, requires a strong emphasis on personal
communication [Kraut, R. E. and Streeter, L. A., "Coordination in software
development," Communications of the ACM, vol. 38, pp. 69-81, 1995]

@@

A key question in this study was the definition of \emph{large scale}. Our goal
was to identify phenomena that appear particularly in large-scale
transformations, and which may not be present in small organizations. Large
scale requires additional coordination and makes communication difficult
compared to software development in small teams. In this section we present the
definition of large scale that is used in this study.

Proceeding a workshop at XP2013 Dingsøyr et al. \cite{Dingsoyr2013} compiled a
description of the definition of large scale. Dingsøyr et al. describe that
at the XP2013 workshop the most common view on large scale was the involvment of
many people. Dingsøyr et al. also conducted a brief literature search to
identify what definitions on large scale are used. The results showed that
large scale had been regadred in terms of size in persons or teams, project
budget, code base size, and project duration. Paasivaara et al.
\cite{Paasivaara2008} referred to an organization of 40 people and 7 teams.
Berger and Beynon-Davies \cite{Berger2009} present the project cost of over £10
million as a factor of large scale, but also highlight a team size of over 50
people. A product with a code base size of over 5 million lines of code was
considered to represent a large scale development effort by Petersen and Wohlin
\cite{Petersen2010}. A project time of 2 years was considered as a factor of
large scale by Bjarnson et al. \cite{Bjarnason2011}, as well as a project scope
of 60-80 features.

--> Needs to have complexity in software design?? --> What is complexity in software?
    Is ``complexity'' an issue in agile?
    What will bring complexity into software? Not costs or the length of the
    schedule. --> Having many people will bring the complexity in terms of the
    SDM to use.
--> Formal definitions (EU, etc.) look at project costs or company turnover.
    These definitions do not take a standpoint on complexity of the product, so
    they do not matter in the context of SDMs.

--> [Cockburn 2003] Agile is best suitable for teams around 50 people or fewer.
--> Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
    Perplexed: Addison-Wesley, 2003. --> There might be a 50 person boundary?
    --> See Boehm also for list of

@@

Transformation and ``scaling up'' of agile practices in use are very closely
related concepts, and in some cases they are one and the same. For instance, if
transformation begins with a pilot and spreads gradually through the
organization, the process can very well be seen as a ``scaling up'' journey.
However, we excluded cases where an initially small organization was scaled up
\cite{Maranzato2012}, and discussions focusing on processes or tools without
describing organizational change \cite{Lyon2008}.
% Also [Greening 2010] on process centered viewpoint without transformation

@@

Further examples on exclusion by the \emph{large scale} facet were cases with
large organizations but only a single team adopting agile \cite{Fulgham2011}.
We considered cases of single teams (although in large organizations) unrelated
to this research as our focus is on transformation of the entire organization.
Also piloting cases that resulted only in single teams using agile were excluded
\cite{Scott2008}. Finally, cases where the organization was growing to large
scale, but did not meet the size criteria at the start of the transformation,
were excluded.

@@

In addition to inter-team coordination there were also other challenges that
should only emerge in a sizable organization.
Most importantly, additional layers of management are usually necessary to steer
large groups of people. The problem is that agile methods provide little
guidance on how to organize management.
Problems may also arise in a large environment if the schedule of agile adoption
varies from team to team. Internal fragmentation is a further problem that may
be encountered in large organizations.
Table \ref{table:challenges_largescale} summarizes these challenges.
